The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-11 src/cover-letter.tex
Remove commenting, add cover letter.

\setkomavar{subject}{%
    The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs
}

@@

    Many thanks for considering our manuscript for possible publication in
    \textit{scientific reports}. Our hope is that modelling the evolution of the
    CoViD-19 pandemic and the relative effectiveness of diverse interventions are of
    interest to a broad readership. We make both methodological and substantive
    contributions.

    We incorporate detailed NPIs, different tests, and vaccinations in an agent-based
    model, taking into account behavioural reactions to symptoms or positive test
    results. Importantly, we do so in a way that allows to calibrate its parameters
    based on routinely available data. We apply the model to the second and third waves
    of the CoViD-19 pandemic in Germany over a period of 9 months, achieving a good fit
    to actual infection rates.

    Our core substantive result is that rapid testing has been very effective relative
    to many NPIs in a low-medium vaccination environment. This is the relevant scenario
    for most countries across the world at present; it seems also applicable to countries
    with high vaccination rates under the conditions of the delta variant.

>>>>

\setkomavar{subject}{%
    The Effectiveness of Testing, Vaccinations, and Contact Restrictions for Containing the Covid-19 Pandemic
}

@@

    Many thanks for inviting a revision of manuscript for possible publication in
    \textit{Scientific Reports}. We are confident that we were able  to address all
    points that have been raised, please see our detailed response.

    We are looking forward to hearing from you.
